Effectful Semantics for Substructural SSA

### 2023-11-16 pldi24/paper.tex
Added addresses, formatted, tap

There have also been many operational semantics for SSA arising from
compiler verification efforts. \citet{barthe-compcert-ssa-2014} give
an operational semantics of SSA as part of the CompCertSSA project,
and prove that the translation from three-address code into SSA is
semantics preserving. \citet{herklotz-gsa-2023} also formalise an
extension to SSA, ``gated SSA'', and give it a semantics, and give
semantics-preserving translations between GSA and ordinary SSA. Going
beyond CompCertSSA, \citet{vellum} have studied the semantics of the LLVM
IR itself.

>>>>

There have also been many operational semantics for SSA arising from
compiler verification efforts. \citet{barthe-compcert-ssa-2014} give
an operational semantics of SSA as part of the CompCertSSA project,
and prove that the translation from three-address code into SSA is
semantics preserving. \citet{herklotz-gsa-2023} also formalise an
extension to SSA, "gated SSA", and give it a semantics, and give
semantics-preserving translations between GSA and ordinary SSA. Going
beyond CompCertSSA, \citet{vellum} have studied the semantics of the LLVM
IR itself.
